Bilderkennung mit Convolutional Neural Networks

### 2018-01-15 presentation_1.tex
inception abschnitt

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

@@

\author{Ivo Tremel und Lennard N\"{o}hren} % Your name
\institute[CHI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Leibniz Universit\"{a}t Hannover \\ % Your institution for the title page
\medskip
%\textit{john@smith.com} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

\subsection{Convolution Layer} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

@@

\subsection{Aufbau}

@@

\begin{frame}
\frametitle{Figure}
Uncomment the code on this slide to include your own image from the same directory as the template .TeX file.
%\begin{figure}
%\includegraphics[width=0.8\linewidth]{test}
%\end{figure}
\end{frame}

@@

\begin{frame}
\Huge{\centerline{Vielen Dank für die Aufmerksamkeit}}
\end{frame}

>>>>

\usepackage{graphicx,caption} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage[utf8]{inputenc} %für ß

@@

\author{Ivo Tremel und Lennard N\"{o}hren} % Your name
\institute[CHI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Leibniz Universit\"{a}t Hannover \\ % Your institution for the title page
\medskip
%\textit{john@smith.com} % Your email address
}
\date{18. Januar 2018} % Date, can be changed to a custom date

@@

\subsection{Convolutional Layer} % A subsection can be created just before a set of slides with a common theme to further break down your presentation into chunks

\begin{frame}
	\frametitle{Covolutional Layer}
\end{frame}

\begin{frame}
	\frametitle{Pooling Layer}
\end{frame}

\begin{frame}
	\frametitle{Aufbau}
\end{frame}

\begin{frame}
	\frametitle{Inception Module}
	\begin{figure}
		\includegraphics[width=0.8\linewidth]{images/inception_meme.jpg}\\
		\hspace*{0pt}\hbox{\scriptsize Quelle:\thinspace{\small\itshape http://knowyourmeme.com/memes/we-need-to-go-deeper}}
	\end{figure}

\end{frame}

\begin{frame}
	\frametitle{Inception Module}
	\begin{columns}[c]
		\column{0.5\textwidth}
		\begin{itemize}
			\item Analyse des Inputs in verschiedenen Skalierungen
			\item F\"{u}r niedrige Level 1x1 Convolution f\"{u}r kleine Features
			\item 3x3 und 5x5 Convolution f\"{u}r gr\"{o}{\ss}ere Features
			\item Max Pooling sehr effektiv in CNN's \\ 
			$\rightarrow$ Als Alternativer Pfad zu Convolutions enthalten
		\end{itemize}

		\column{0.5\textwidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{images/inception_naive_graph.png}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Inception Module}
	\begin{columns}[c]
		\column{0.5\textwidth}
		\begin{itemize}
			\item Sehr hoher Rechenaufwand
			\item Dimension steigt stark an
			\item Deshalb: 1x1 Convolutions vor den größeren Modulen
			\item Reduziert die Dimension des Inputs
			\item Erm\"{o}glicht mehrere Inception Module in Folge 
		\end{itemize}

		\column{0.5\textwidth}
		\begin{figure}
			\includegraphics[width=\linewidth]{images/inception_pro_graph.png}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Aufbau}
	\begin{figure}
		\includegraphics[width=0.4\linewidth]{images/main_graph_inception_reduced.png}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Datensatz}
\end{frame}

\begin{frame}
	\frametitle{Ergebnisse}
\end{frame}

\begin{frame}
	\frametitle{Diskussion}
\end{frame}

\begin{frame}
	\frametitle{Zusammenfassung und Ausblick}
\end{frame}

%------------------------------------------------
%hiernach kommen die besipiele wie man verschiedene sachen in LaTex macht
%------------------------------------------------

@@

@@

\begin{frame}
	\frametitle{Figure}
	Uncomment the code on this slide to include your own image from the same directory as the template .TeX file.
	\begin{figure}
		\includegraphics[width=0.4\linewidth]{images/main_graph_inception_reduced.png}
	\end{figure}
\end{frame}

@@

\begin{frame}
\Huge{\centerline{Vielen Dank f\"{u}r die Aufmerksamkeit}}
\end{frame}
